Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-13 draft.tex
new reference for human comprehension of fake voice samples

		Cursory research \cite{sharevski_blind_2024} is already present into what factors humans
		use to identify fake and real audio samples, as well as their performance, but the named
		aspects of the samples have not yet been mapped to such perceptible features as the ones
		used in this method, leaving the question of the usability of such explanations open.
		Finally, we have not addressed in our experiments how the features can be presented to the
		end user. Certain implementations of LIME already have means to present their results
		graphically, but the effectiveness of such methods has yet to be studied.

>>>>

		Cursory research \cite{warren_better_2024,sharevski_blind_2024} is already present into
		what factors humans use to identify fake and real audio samples, as well as their
		performance, but the named aspects of the samples have not yet been mapped to such
		perceptible features as the ones used in this method, leaving the question of the
		usability of such explanations open. Finally, we have not addressed in our experiments how
		the features can be presented to the end user. Certain implementations of LIME already
		have means to present their results graphically, but the effectiveness of such methods has
		yet to be studied.
